### 2013-08-05 Docs/runtime_parameters/runtime_parameters.tex
update + fix path to _parameters

@@

@@

\rowcolor{tableShade}
\verb=  cg_verbose  = &   Verbosity of bottom solver  &  0 \\
\verb=  hg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\
\rowcolor{tableShade}
\verb=  hg_dense_stencil  = &   In hgproject, in 2D, use a 9 point Laplacian (.true.) or 5-point Laplacian (.false.).  In 3D, use a 27 point Laplacian (.true.) or 7-point Laplacian (.false.).  &  .true. \\
\verb=  max_mg_bottom_nlevels  = &   if mg\_bottom\_solver == 4, then how many mg levels can the bottom solver mgt object have  &  1000 \\
\rowcolor{tableShade}
\verb=  mg_bottom_nu  = &   number of smoothing iterations to do after the multigrid bottom solver  &  10 \\
\verb=  mg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\
\rowcolor{tableShade}
\verb=  mg_verbose  = &   Verbsoity of the multigrid solver, but not the bottom solver.  &  0 \\
\verb=  use_hypre  = &   use the hypre library  &  .false. \\

@@

\rowcolor{tableShade}
\verb=  conductivity_constant  = &   the constant conductivity (only applies if the conductivity/constant module is used)  &  1.0d0 \\
\verb=  temp_diffusion_formulation  = &   How to compute the explicit thermal diffusion term.  \newline 1 = in terms of $T$; \newline 2 = in terms of $\rho,p_0,X$.  &  2 \\
\rowcolor{tableShade}
\verb=  thermal_diffusion_type  = &   In the thermal diffusion solver, 1 = Crank-Nicholson; 2 = Backward Euler.  &  1 \\
\verb=  use_thermal_diffusion  = &   Use thermal diffusion.  &  .false. \\

>>>>

\verb=  ppm_trace_forces  = &   if 1, then perform parabolic reconstruction on the forces used in the prediction and trace under the parabola to the interfaces the amount that can reach the interface over dt  &  0 \\

@@

\verb=  stop_initial_convection  = &   timestep beyond which we set {\tt drive\_initial\_convection} = F  &  -1 \\

@@

\rowcolor{tableShade}
\verb=  cg_verbose  = &   Verbosity of bottom solver  &  0 \\
\verb=  hg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\
\rowcolor{tableShade}
\verb=  hg_cycle_type  = &   Type of cycle used in the nodal multigrid -- 1 = F-cycle, 2 = W-cycle, 3 = V-cycle  &  3 \\
\verb=  hg_dense_stencil  = &   In hgproject, in 2D, use a 9 point Laplacian (.true.) or 5-point Laplacian (.false.).  In 3D, use a 27 point Laplacian (.true.) or 7-point Laplacian (.false.).  &  .true. \\
\rowcolor{tableShade}
\verb=  max_mg_bottom_nlevels  = &   if mg\_bottom\_solver == 4, then how many mg levels can the bottom solver mgt object have  &  1000 \\
\verb=  mg_bottom_nu  = &   number of smoothing iterations to do after the multigrid bottom solver  &  10 \\
\rowcolor{tableShade}
\verb=  mg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\
\verb=  mg_cycle_type  = &   Type of cycle used in the MAC multigrid -- 1 = F-cycle, 2 = W-cycle, 3 = V-cycle  &  3 \\
\rowcolor{tableShade}
\verb=  mg_nu_1  = &   number of smoothing iterations to do going down the V-cycle  &  2 \\
\verb=  mg_nu_2  = &   number of smoothing iterations to do going up the V-cycle  &  2 \\
\rowcolor{tableShade}
\verb=  mg_verbose  = &   Verbsoity of the multigrid solver, but not the bottom solver.  &  0 \\
\verb=  use_hypre  = &   use the hypre library  &  .false. \\

@@

\rowcolor{tableShade}
\verb=  conductivity_constant  = &   the constant conductivity (only applies if the conductivity/constant module is used)  &  1.0d0 \\
\verb=  limit_conductivity  = &   apply the conductivity limiting---if T, then we set the thermal coefficients all to 0 for $\rho <$ {\tt buoyancy\_cutoff\_factor} * {\tt base\_cutoff\_density}  &  .false. \\
\rowcolor{tableShade}
\verb=  temp_diffusion_formulation  = &   How to compute the explicit thermal diffusion term.  \newline 1 = in terms of $T$; \newline 2 = in terms of $\rho,p_0,X$.  &  2 \\
\verb=  thermal_diffusion_type  = &   In the thermal diffusion solver, 1 = Crank-Nicholson; 2 = Backward Euler.  &  1 \\
\rowcolor{tableShade}
\verb=  use_thermal_diffusion  = &   Use thermal diffusion.  &  .false. \\
